Global code motion of congruent instructions

### 2017-04-18 paper.tex
mention unit for code size decrease

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
                &\% performance uplift & \% code size decrease & \% code size decrease\\
Benchmarks      & at -Ofast (high better)& at -Ofast (high better) & at -Os (high better)\\\hline
400.perlbench	& 1.00  & -9120  & 544  \\\hline
401.bzip2	& 1.00  & -1600  & 128  \\\hline
403.gcc	        & 1.00  & -58176 & 3384 \\\hline
429.mcf	        & 1.03  & 160    & 16   \\\hline
433.milc	& 1.00  & -656   & 224  \\\hline
444.namd	& 1.00  & -3864  & -1168\\\hline
445.gobmk	& 0.99  & -20480 & -264 \\\hline
447.dealII	& 0.95  & -27836 & 50934\\\hline
450.soplex	& 0.99  & 2220   & 348  \\\hline
453.povray	& 0.97  & 164    & -472 \\\hline
456.hmmer	& 0.99  & -3464  & -352 \\\hline
458.sjeng	& 1.02  & 440    & 1456 \\\hline
462.libquantum	& 1.00  & -96    & 0    \\\hline
464.h264ref	& 1.00  & -3424  & 864  \\\hline
470.lbm	        & 1.00  & 0      & 0    \\\hline
471.omnetpp	& 1.00  & 2688   & 200  \\\hline
473.astar	& 1.00  & -928   & 152  \\\hline
482.sphinx3	& 0.99  & 3008   & -176 \\\hline
483.xalancbmk	& 1.01  & 46492  & 4012 \\\hline
Geomean         & 0.997 &  & \\\hline
    \end{tabular}
  \end{center}
  \caption{Execution time (ratio) and code size change (bytes) with and without
    \gcm{} (\GCM{}) on \SPEC{}: performance uplift at -Ofast in mcf and sjeng;
    code size improvement in dealII at -Os.}
  \label{tab:code-size}
\end{table}

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
                &\% performance uplift & size decrease in Bytes & size decrease in Bytes\\
Benchmarks      & at -Ofast (high better)& at -Ofast (high better) & at -Os (high better)\\\hline
400.perlbench	& 1.00  & -9120  & 544  \\\hline
401.bzip2	& 1.00  & -1600  & 128  \\\hline
403.gcc	        & 1.00  & -58176 & 3384 \\\hline
429.mcf	        & 1.03  & 160    & 16   \\\hline
433.milc	& 1.00  & -656   & 224  \\\hline
444.namd	& 1.00  & -3864  & -1168\\\hline
445.gobmk	& 0.99  & -20480 & -264 \\\hline
447.dealII	& 0.95  & -27836 & 50934\\\hline
450.soplex	& 0.99  & 2220   & 348  \\\hline
453.povray	& 0.97  & 164    & -472 \\\hline
456.hmmer	& 0.99  & -3464  & -352 \\\hline
458.sjeng	& 1.02  & 440    & 1456 \\\hline
462.libquantum	& 1.00  & -96    & 0    \\\hline
464.h264ref	& 1.00  & -3424  & 864  \\\hline
470.lbm	        & 1.00  & 0      & 0    \\\hline
471.omnetpp	& 1.00  & 2688   & 200  \\\hline
473.astar	& 1.00  & -928   & 152  \\\hline
482.sphinx3	& 0.99  & 3008   & -176 \\\hline
483.xalancbmk	& 1.01  & 46492  & 4012 \\\hline
Geomean         & 0.997 &  & \\\hline
    \end{tabular}
  \end{center}
  \caption{Execution time (ratio) and code size change (bytes) with and without
    \gcm{} (\GCM{}) on \SPEC{}: performance uplift at -Ofast in mcf and sjeng;
    code size improvement in dealII at -Os.}
  \label{tab:code-size}
\end{table}
